Boosted Regression Trees for Predictive Auto-Tuning

### 2011-12-13 paper/draft1.tex
Last brain dump edits... ready to go to writing mode... 4096 childrennnn ! ! !

>>>>

XXX: deliver significant performance increases at very low run-time cost (less
than a second if the input domain has not been seen before, zero if it
has, since it will hit the cache) compared with the reference
implementation

XXX always delivered good performance: optimality without loss of productivity?

XXX such machine learning derived model-based empirical auto-tuner hold great
promise for dev productivity, portability, performance on future multi-core hw
with different architectural features

XXX frameworks for predicting performance exist \cite{XXX Hwu An Adaptive
Performance Modeling Tool for GPU Architectures}
but for non-GPU architectures
